Parameter Estimation for the CES Model

### 2013-07-23 CES.Rnw
Created a modelMatrix. Added template of code to extract coefficients from modelMatrix.

# Now, extract coefficients to make a table
coef(kleModels["US"])
@

>>>>

modelMatrix <- cbind(kleModels, lekModels, eklModels)
colnames(modelTable) <- nestingOptions

# Now, extract coefficients from each model in the matrix
# to make data.frames of coefficients. Each data.frame has 
# countries in rows and nesting options in columns 
# (same structure) as modelMatrix

# gamma

# lambda

# delta

# delta1

# rho

# rho1

@
